Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-10 talk/vmil2012/paper.tex
add a todo
Write about the guard failure frequency

\section{Evaluation}
\label{sec:evaluation}

@@

\subsection{Guard Failures}
\label{sub:guard_failure}
\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards}
    \label{fig:failing_guards}
\end{figure}

>>>>

\section{Evaluation}
\label{sec:evaluation}
\todo{improve the table formatting}

@@

\subsection{Guard Failures}
\label{sub:guard_failure}
The last point in this discussion is the frequency of guard failures.
Figure~\ref{fig:failing_guards} presents for each benchmark a list of the
relative amounts of guards that ever fail and of guards that fail more than 200
times. For guards that fail more than 200 times, as described before, a trace
is recorded that starts from the guard, patching the guard so that later
failures execute the new trace instead of taking the side-exit. Hence the
numbers presented for guards that fail more than 200 times represent the 200
failures up to the compilation of the bridge and all executions of the then
attached bridge.

\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards}
    \label{fig:failing_guards}
\end{figure}

From Figure~\ref{fig:failing_guards} we can see that only a very small amount
of all the guards in the optimized traces ever fail. This amount varies between
2.4\% and 5.7\% of all guards. As can be expected, even less guards fail often
enough that a bride is compiled for them, only 1.2\% to 3.6\% of all guards
fail more than 200 times. Also of all failing guards a few fail extremely often
and most fail rarely. The results emphasizes that as most of the guards never
fail it is important to make sure that the successful execution of a guard does
not have unnecessary overhead.
